Original Beyond Ultra-Diffuse Galaxies: Mass-Size Outliers in the Satellites of Milky Way Analogs

### 2022-10-12 paper0.tex
done except for discussion section
before sending to coauthors

% \title{Ultra Diffuse Galaxies associated with Milky-Way Analogs}
\title{Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers in the Satellites of Milky Way Analogs}

@@

Different mechanisms are proposed to explain the presence of large diffuse galaxies in different environments. In the field (i.e, in isolation), their large sizes might be caused by star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}. In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019} or via adiabatic expansion due to mass loss \citep{Tremmel2020}. Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed and quenched. It is also unclear whether mass-size outliers belong to a special class of galaxies or are just a natural extension of dwarf systems to lower surface brightness. To answer these questions, we can compare mass-size outliers with ``normal'' low mass galaxies for which we have a better understanding.

>>>>

% \title{Ultra Diffuse Galaxies associated with Milky-Way Analogs}
\title{Original Beyond Ultra-Diffuse Galaxies: Mass-Size Outliers in the Satellites of Milky Way Analogs}

@@

Different mechanisms are proposed to explain the presence of large diffuse galaxies in different environments. In the field (i.e, in isolation), their large sizes might be caused by star-formation feedback \citep{DiCintio2017,Chan2018}, early galaxy mergers \citep{Wright2021}, passing into and out of a more massive halo (so-called backsplash satellites, \citealt{Benavides2021}), or by inhabiting halos with higher spin \citep{Dalcanton1997,Amorisco2016,Liao2019,Benavides2022}. In groups and clusters, their large sizes may ensue from tidal heating near pericenter \citep{Jiang2019} or via adiabatic expansion due to mass loss \citep{Tremmel2020}. Despite theoretical advances, it is still an open question how mass-size outliers like UDGs are formed and quenched. It is also unclear whether mass-size outliers belong to a distinct class of galaxies or are just a natural extension of dwarf systems to lower surface brightness. To answer these questions, we can compare mass-size outliers with ``normal'' low mass galaxies for which we have a better understanding.
